Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
Adding figure

\note{TR: put this into a proper figure, add known danvy sequence
for concrete evaluators at the bottom (in grey or dashed lines)}

\begin{tikzpicture}
  \matrix (m) [matrix of math nodes, row sep=2.5em, column sep=3.7em]
    {
        &  &  &  &
      \begin{smallmatrix} \text{abstract} \\ \text{definitional} \\ \text{interpreters} \end{smallmatrix} \\
      \begin{smallmatrix} \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
      \begin{smallmatrix} \text{big-step} \\ \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix}  &
      \begin{smallmatrix} \text{disentangled}  \\ \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
      \begin{smallmatrix} \text{refunctionalized}  \\ \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
      \begin{smallmatrix} \text{monadic} \\ \text{abstracting} \\ \text{definitional} \\ \text{interpreters} \end{smallmatrix}  \\
      \begin{smallmatrix} \text{abstract} \\ \text{machines} \end{smallmatrix} &
        &
      %\begin{smallmatrix} \text{big-step} \\ \text{abstract} \\ \text{machines} \end{smallmatrix}  &
        &
      %\begin{smallmatrix} \text{disentangled} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
        &
      %\begin{smallmatrix} \text{refunctionalized} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
      \begin{smallmatrix} \text{definitional} \\ \text{interpreters} \end{smallmatrix} \\
    };
  {
    [start chain] \chainin (m-2-4);
    \chainin (m-1-5) [join={node[sloped,anchor=center,above,labeled] {\text{un-CPS}}}];
    \chainin (m-2-5) [join={node[above,labeled] {\text{}}}];
    \chainin (m-1-5) [join={node[above,labeled] {\text{}}}];
  }
  {
    [start chain] \chainin (m-2-1);
    \chainin (m-2-2) [join={node[above,labeled] {\begin{smallmatrix} \text{linearizing} \\ \text{+} \\ \text{fusing} \end{smallmatrix}}     }];
    \chainin (m-2-3) [join={node[above,labeled] {\text{disentangling}}}];
    \chainin (m-2-4) [join={node[above,labeled] {\text{refunc.}}}];
    \chainin (m-2-5) [join={node[above,labeled] {\text{monadify}}}];
  }
  {
    [start chain]
    \chainin (m-3-1);
    { [start branch=A] \chainin (m-2-1)
      [join={node[left, labeled] {\alpha}}];
    }
  }
    %\chainin (m-2-2);
    %\chainin (m-2-3);
    %\chainin (m-2-4);
  {
    [start chain]
    \chainin (m-3-5);
    { [start branch=B] \chainin (m-2-5)
      [join={node[right, labeled] {\alpha}}];
    }
  }
\end{tikzpicture}

>>>>

% \note{TR: put this into a proper figure, add known danvy sequence
% for concrete evaluators at the bottom (in grey or dashed lines)}

\begin{figure}
\begin{center}
\includegraphics[width=100mm,scale=1.0]{figures/lines.png}
\end{center}
\end{figure}

% \begin{tikzpicture}
%   \matrix (m) [matrix of math nodes, row sep=2.5em, column sep=3.7em]
%     {
%         &  &  &  &
%       \begin{smallmatrix} \text{abstract} \\ \text{definitional} \\ \text{interpreters} \end{smallmatrix} \\
%       \begin{smallmatrix} \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
%       \begin{smallmatrix} \text{big-step} \\ \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix}  &
%       \begin{smallmatrix} \text{disentangled}  \\ \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
%       \begin{smallmatrix} \text{refunctionalized}  \\ \text{abstract} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
%       \begin{smallmatrix} \text{monadic} \\ \text{abstracting} \\ \text{definitional} \\ \text{interpreters} \end{smallmatrix}  \\
%       \begin{smallmatrix} \text{abstract} \\ \text{machines} \end{smallmatrix} &
%         &
%       %\begin{smallmatrix} \text{big-step} \\ \text{abstract} \\ \text{machines} \end{smallmatrix}  &
%         &
%       %\begin{smallmatrix} \text{disentangled} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
%         &
%       %\begin{smallmatrix} \text{refunctionalized} \\ \text{abstract} \\ \text{machines} \end{smallmatrix} &
%       \begin{smallmatrix} \text{definitional} \\ \text{interpreters} \end{smallmatrix} \\
%     };
%   {
%     [start chain] \chainin (m-2-4);
%     \chainin (m-1-5) [join={node[sloped,anchor=center,above,labeled] {\text{un-CPS}}}];
%     \chainin (m-2-5) [join={node[above,labeled] {\text{}}}];
%     \chainin (m-1-5) [join={node[above,labeled] {\text{}}}];
%   }
%   {
%     [start chain] \chainin (m-2-1);
%     \chainin (m-2-2) [join={node[above,labeled] {\begin{smallmatrix} \text{linearizing} \\ \text{+} \\ \text{fusing} \end{smallmatrix}}     }];
%     \chainin (m-2-3) [join={node[above,labeled] {\text{disentangling}}}];
%     \chainin (m-2-4) [join={node[above,labeled] {\text{refunc.}}}];
%     \chainin (m-2-5) [join={node[above,labeled] {\text{monadify}}}];
%   }
%   {
%     [start chain]
%     \chainin (m-3-1);
%     { [start branch=A] \chainin (m-2-1)
%       [join={node[left, labeled] {\alpha}}];
%     }
%   }
%     %\chainin (m-2-2);
%     %\chainin (m-2-3);
%     %\chainin (m-2-4);
%   {
%     [start chain]
%     \chainin (m-3-5);
%     { [start branch=B] \chainin (m-2-5)
%       [join={node[right, labeled] {\alpha}}];
%     }
%     {
%       [start branch=D, color=gray] \chainin (m-3-1)
%       [join={node[right, labeled] {\text{}}}];
%     }
%   }
%   {
%     [start chain, color=gray] \chainin (m-3-1);
%     {
%       [start branch=C] \chainin (m-3-5)
%       [join={node[above, labeled] {\text{Known Danvy Sequence for Concrete Evaluators}}}];
%     }
%   }
% \end{tikzpicture}
